---
title: "Slidify"
author: "Rafael Reséndiz, Proffesor of Educative Assesment"
highlighter: highlight.js
output:
  html_document:
    keep_md: yes
    number_sections: yes
    toc: yes
job: UABC, Xochicalco
knit: slidify::knit2slides
mode: selfcontained
hitheme: tomorrow
subtitle: Data meets presentation
framework: io2012
widgets: []
---

## **Reproducible Pitch Presentation**


### 1. Knowing "Data meets presentation"
### 2. Statistical inference and simulation
### 3. Data basic plot
### *  Hiperlink a Rpubs (http://rpubs.com/Rafael-Resendiz/RPP)


--- .class #id 

## 1. Knowing "Data meets presentation"

Load files and datasets and and have fun with them
```{r}
data(iris)  # Load data
lm(iris)    # Make a lineal regression
```

--- .class #id 


## 2. Statistical inference and simulation
Setting the global options
Example: The exponential distribution
```{r}
lambda = 0.2           # lambda for all simulations
n = 40                 # number of exponential random variables
nsims = 1:10000        # number of simulated averages
set.seed(901)
means <- data.frame(x=sapply(nsims,function(x) {mean(rexp(n,lambda))})) # necessary means
head(means,2)          # show the results
str(means)             # See a summary of the results
```

--- .class #id 


## Statistical inference in the real life

```{r}
fit <- lm(iris)   # Work with real data
confint(fit)      # Identify intercepts and others
summary(fit$residuals)
```

--- .class #id 
## Data basic plot
Plot your results and identify your creativity
```{r, echo=FALSE}
library(ggplot2)
ggplot(data = means, aes(x = x)) +
geom_histogram(aes(y=..density..), fill = I('#00e6ff'),
binwidth = 0.1, color = I('red')) +
stat_function(fun = dnorm, arg = list(mean = 5, sd = sd(means$x)))
```
